Hypercoercions and a Framework for Equivalence of Cast Calculi

### 2019-10-27 paper.tex
define env for S(C)
Further explain results the applyCast function.

\begin{proposition}[$L$ Properties]\label{thm:L-LazyD-monoid}\ 
  \begin{enumerate}
  \item $L$ is an instance of the Lazy D ADT
  \item $L$ is a monoid
  \item $cast(T,l,T) = id(T)$
  \end{enumerate}
\end{proposition}
\begin{proof}
  Part (1) is straightforward because property (1) and (2) are 
  trivially true and because $appS$ effectively repeats property (3) - 
  (11).
  Part (2) is true because list is known to be a monoid.
  Part (3) follows immediately from the definition of $cast(T,l,T)$
\end{proof}

@@

\figref{hc-applyCast} defines $applyCast(v,c)$ for \lazyD\ hypercoercions. 
Applying the identity cast for the 
dynamic type succeeds immediately. Otherwise, we firstly 
apply the middle, then apply the tail. We denote by $r \; >>= \; f$ to mean 
that if $r$ is $\rOOsucc{v}$, the result is $f(v)$, otherwise, the result 
is the failure.
$ applyMiddle(v,\ell,m)$ and $applyTail(v,t)$ are straightforward.
In the definition of $applyMiddle(v,\ell,m)$, we generalize 
shallow-consistency to compare middles and values ($v \smile m$) in the 
obvious way.

@@

%% Appendix
\appendix
\section{Appendix}

Text of appendix \ldots

>>>>

\begin{proposition}[$L$ Properties]\label{thm:L-LazyD-monoid}\ 
  \begin{enumerate}
  \item $L$ is an instance of the Lazy D ADT
  \item $L$ is a monoid
  \item $cast(T,l,T) = id(T)$
  \end{enumerate}
\end{proposition}
\begin{proof}
  Part (1) is straightforward because property (1) and (2) are 
  trivially true and because $appS$ effectively repeats property (3) - 
  (11).
  Part (2) is true because lists are known to be a monoid with respect to append.
  Part (3) follows immediately from the definition of $cast(T,l,T)$
\end{proof}

@@

\figref{hc-applyCast} defines $applyCast(v,c)$ for \lazyD\ hypercoercions.
Applying the identity cast for the dynamic type succeeds immediately. If the
value is injected and the cast is not the identity cast, then $applyCast$
projects the value and relies on $applyMiddle$ to ensure that value is shallow
consistent with target type of the head. Regardless of whether or not the value
is projected, $applyCast$ applies the middle, then apply the tail if the middle
succeeds. We denote by $r \; >>= \; f$ to mean that if $r$ is $\rOOsucc{v}$, the
result is $f(v)$, otherwise, the result is the failure. In the definition of
$applyMiddle(v,\ell,m)$, we generalize shallow-consistency to compare middles
and values ($v \smile m$) in the obvious way. When a value is shallowly
inconsistent from the middle, it is the result of projecting a value that was
shallowly inconsistent with the expected type of the projection in the head. Thus, a
blame label $l$ must have been pass in as $\ell$ and is to blame. Finally if a
failure in $applyMiddle$ has not occurred then $applyTail(v, t)$ interprets the
tail, $t$, to the appropriate cast of the value $v$.

@@

%% Appendix
% \appendix
% \section{Appendix}

% Text of appendix \ldots
